
\begin{enumerate}
\item Solve the following inequation and write down the solution set:\\
\begin{align}	
      11x-4<15x+4 \leq 13x+14,x\in W
\end{align}
\text Represent the solution on a real number line.
\item Solve for $x$ the quadratic equation $x^2 - 4x-8 = 0$.\\
Give your answer correct to three significant figures.
\item Using the factor theorem, show that \brak{x-2} is a factor of $ x^3+x^2-4x-4$.\\
	Hence factorise the polynomial completely.
\item Using the Remainder Theorem find the remainders obtained when $x^3+\brak{kx+8}x+k$ is divided by $x+1$ and $x-2$.\\
Hence find $\textbf{k}$ if the sum of the two remainders is $1$.
\item In an Arithmetic Progression \brak{A.P.} the fourth and sixth terms are $8$ and $14$ respectively.Find the:
	\begin{enumerate}
	\item first term 
	\item common difference
	\item sum of the first $20$ terms.
	\end{enumerate}
\item The first and last term of a Geometrical Progression \brak{G.P.} are $3$ and $96$ respectively. If the common ratio is $2$, find:
\begin{enumerate}
    \item \textbf{n'} the number of terms of the G.P.
    \item Sum of the $\textbf{n}$ terms.
\end{enumerate}
\item The sum of the first three terms of an Arithmetic Progression \brak{A.P.} is $42$ and the product of the first and third term is $52$. Find the first term and the common difference. 
  
\item Using properties of proportion solve for$x$,given
\begin{align}
    \frac{\sqrt{5x}+\sqrt{2x-6}}{\sqrt{5x}-\sqrt{2x-6}}=4
\end{align}

\item The product of two consecutive natural numbers which are multiples of $3$ is equal to $810$.Find the two numbers.
\end{enumerate}

